---
title: "Reaction Time Descriptive Analysis"
author: "Ian McCarthy"
date: "2024-01-12"
output: html_document
---





Installing necessary packages and conversions

```{r}

library(tidyverse)
library(R.matlab)
library(matlib)
library(readr)

```

Big loops to get all data into their respective sessions and altering any errors
When running, make sure fmri1 has 34, 2 has 31, training has 34. Sometimes it messes up with the subject 9 stuff

```{r}


#fmri1 data
mat.fMRI1 <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S\\d+_fMRI1_r3_\\d+-\\d+.mat$", 
                        full.names = TRUE)

#fmri2 data
mat.fMRI2 <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S\\d+_fMRI2_r3_\\d+-\\d+.mat$", 
                        full.names = TRUE)

#training data - creates duplicates? figure out
mat.training <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S\\d+_training_r3_\\d+-\\d+.mat$", 
                        full.names = TRUE)

#S05_fmri1_r1 and s45_fmri2_r1
mat.errors <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S05_fMRI1_r1_\\d+-\\d+.mat$|CA2step_S45_fMRI2_r1_\\d+-\\d+.mat$|CA2step_S45_fMRI2_r2_\\d+-\\d+.mat$", 
                        full.names = TRUE)

##fmri1 loop

for (x in mat.fMRI1) {
  
  #creates file name matching the matlab file name without .mat
  file_name <- tools::file_path_sans_ext(basename(x))
  
  #convert data into r
  mat_data <- readMat(x)
  
  #assigns the file name to each individual participant in the list
  assign(file_name, mat_data)
  
  #create list of data
  
    env <- ls() #current environment
    fmri1_participants <- c(env[grep(pattern = "CA2step_S\\d+_fMRI1_r3_\\d+-\\d+$|CA2step_S09_fMRI2_r3_20230505-1347", ls())]) #take the participants matching pattern in env
    fmri1_list <- list() #empty list for loop
  
    #for everyone in the fmri1 participants, put them in a list
    for (i in fmri1_participants){
    
     fmri1_list[[i]] <- get(i)
    
      }
  
  #confirmation message
  cat("Converted and stored", x, "as", file_name, "in R environment. \n")

}

fmri1_list <- fmri1_list[-19] #get rid of s24
fmri1_list <- fmri1_list[-2]  #get rid of s01_0508 since that's actually S09_fmri2


#adding in missing data
s05_fmri1_r1 <- readMat(mat.errors[1])

fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[3]] <- s05_fmri1_r1[["data"]][[3]]
fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[4]] <- s05_fmri1_r1[["data"]][[4]]
fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[5]] <- s05_fmri1_r1[["data"]][[5]]
fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[6]] <- s05_fmri1_r1[["data"]][[6]]



##fmri2 loop

for (x in mat.fMRI2) {
  
  #creates file name matching the matlab file name without .mat
  file_name <- tools::file_path_sans_ext(basename(x))
  
  #convert data into r
  mat_data <- readMat(x)
  
  #assigns the file name to each individual participant in the list
  assign(file_name, mat_data)
  
  #create list of data
  
    env <- ls() #current environment
    fmri2_participants <- c(env[grep(pattern = "CA2step_S\\d+_fMRI2_r3_\\d+-\\d+$|CA2step_S01_fMRI1_r3_20230508-1206",
                            ls())]) #take the participants matching pattern in env
    fmri2_list <- list() #empty list for loop
  
    #for everyone in the fmri1 participants, put them in a list
    for (i in fmri2_participants){
    
     fmri2_list[[i]] <- get(i)
    
      }
  
  #confirmation message
  cat("Converted and stored", x, "as", file_name, "in R environment. \n")

}

#take out current S09 (0505) since it's the wrong one
fmri2_list <- fmri2_list[-9]

#adding in missing data

s45_fmri2_r1 <- readMat(mat.errors[2])
s45_fmri2_r2 <- readMat(mat.errors[3])

fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[1]] <- s45_fmri2_r1[["data"]][[1]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[2]] <- s45_fmri2_r1[["data"]][[2]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[3]] <- s45_fmri2_r1[["data"]][[3]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[4]] <- s45_fmri2_r1[["data"]][[4]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[5]] <- s45_fmri2_r1[["data"]][[5]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[6]] <- s45_fmri2_r1[["data"]][[6]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[12]] #template is missing, take it from the template (check date)


##training loop

for (x in mat.training) {
  
  #creates file name matching the matlab file name without .mat
  file_name <- tools::file_path_sans_ext(basename(x))
  
  #convert data into r
  mat_data <- readMat(x)
  
  #assigns the file name to each individual participant in the list
  assign(file_name, mat_data)
  
  #create list of data
  
  env <- ls() #current environment
  training_participants <- env[grep(pattern = "CA2step_S\\d+_training_r3_\\d+-\\d+$", ls())] #take the participants matching pattern in env
  training_list <- list() #empty list for loop
  
  #for everyone in the fmri1 participants, put them in a list
  for (i in training_participants){
    
    training_list[[i]] <- get(i)
    
  }
  
  #taking out all duplicates and bad ones
  
  training_error <- c(-45, -43, -40, -37, -36, -28, -27, -25, -23, -22, -19, -18, -2, -3, -4, -7, -23, -31)
  
  for (z in training_error) {
    
    training_list <- training_list[z]
  }
  
  #confirmation message
  cat("Converted and stored", x, "as", file_name, "in R environment. \n")
  
}
```
    
Getting together transitions, reallocations, and reaction times
```{r}
#creating vectors of the transitions and reallocation to identify trial type
training_transitions <- all_data[["training"]][["CA2step_S01_training_r3_20221021-1222"]][["expe"]][[1]][[5]]
training_reallocations <- all_data[["training"]][["CA2step_S01_training_r3_20221021-1222"]][["expe"]][[1]][[6]]
fmri1_transitions <- `CA2step_S01_fMRI1_r3_20230316-1704`[["expe"]][[1]][[5]]
fmri1_reallocataions <- `CA2step_S01_fMRI1_r3_20230316-1704`[["expe"]][[1]][[6]]
fmri2_transitions <- `CA2step_S02_fMRI2_r3_20230509-1300`[["expe"]][[1]][[5]]
fmri2_reallocataions <- `CA2step_S02_fMRI2_r3_20230509-1300`[["expe"]][[1]][[6]]

#creating list of empty vectors for the loops
fmri1_stage1_rt <- vector(mode = "list", length = 34)
fmri2_stage1_rt <- vector(mode = "list", length = 34)
training_stage1_rt <- vector(mode = "list", length = 34)

fmri1_stage2_rt <- vector(mode = "list", length = 34)
fmri2_stage2_rt <- vector(mode = "list", length = 34)
training_stage2_rt <- vector(mode = "list", length = 34)

#assigning reaction times to their 
for (x in 1:length(fmri1_list)){
  
  fmri1_stage1_rt[[x]] <- c(fmri1_list[[x]][["data"]][[5]][[4]],
                            fmri1_list[[x]][["data"]][[11]][[4]], 
                            fmri1_list[[x]][["data"]][[17]][[4]])
  
  fmri1_stage2_rt[[x]] <- c(fmri1_list[[x]][["data"]][[6]][[4]],
                            fmri1_list[[x]][["data"]][[12]][[4]], 
                            fmri1_list[[x]][["data"]][[18]][[4]])
  
  training_stage1_rt[[x]] <- c(training_list[[x]][["data"]][[3]][[4]], 
                               training_list[[x]][["data"]][[7]][[4]], 
                               training_list[[x]][["data"]][[11]][[4]])
  
  training_stage2_rt[[x]] <- c(training_list[[x]][["data"]][[4]][[4]], 
                               training_list[[x]][["data"]][[8]][[4]], 
                               training_list[[x]][["data"]][[12]][[4]])
  
}
#fixing the 120 vector in trianing30
training_stage1_fix <- c(rep(NaN,60), training_stage1_rt[[30]])
training_stage2_fix <- c(rep(NaN,60), training_stage2_rt[[30]])
training_stage1_rt[[30]] <- training_stage1_fix
training_stage2_rt[[30]] <- training_stage2_fix


fmri2_rt_indices <- c(2:8,10:13,16:34) #those with good data
fmri2_list_indices <- c(2:31)

#those with missing data
fmri2_stage1_rt[[1]] <- rep(NaN, 180) 
fmri2_stage2_rt[[1]] <- rep(NaN, 180)
fmri2_stage1_rt[[14]] <- rep(NaN, 180) 
fmri2_stage2_rt[[14]] <- rep(NaN, 180)
fmri2_stage1_rt[[15]] <- rep(NaN, 180) 
fmri2_stage2_rt[[15]] <- rep(NaN, 180)

#since s09 is stored as s01
fmri2_stage1_rt[[9]] <- c(fmri2_list[[1]][["data"]][[5]][[4]],
                            fmri2_list[[1]][["data"]][[11]][[4]], 
                            fmri2_list[[1]][["data"]][[17]][[4]])
fmri2_stage2_rt[[9]] <- c(fmri2_list[[1]][["data"]][[6]][[4]],
                            fmri2_list[[1]][["data"]][[12]][[4]], 
                            fmri2_list[[1]][["data"]][[18]][[4]])

for (i in fmri2_list_indices){
  for (x in fmri2_rt_indices){
  
  fmri2_stage1_rt[[x]] <- c(fmri2_list[[i]][["data"]][[5]][[4]],
                            fmri2_list[[i]][["data"]][[11]][[4]], 
                            fmri2_list[[i]][["data"]][[17]][[4]])
  
  fmri2_stage2_rt[[x]] <- c(fmri2_list[[i]][["data"]][[6]][[4]],
                            fmri2_list[[i]][["data"]][[12]][[4]], 
                            fmri2_list[[i]][["data"]][[18]][[4]])

  }
}

#these participants' data stored differently, so indexing separately
fmri2_stage1_rt[[32]] <- c(fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[5]][[4]],
                                fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[10]][[4]],
                                fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[16]][[4]])
fmri2_stage2_rt[[32]] <- c(fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[6]][[4]],
                                fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[11]][[4]],
                                fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[17]][[4]])

RT <- list("Stage 1" = list(fmri1_stage1_rt, fmri2_stage1_rt, training_stage1_rt),
           "Stage 2" = list(fmri1_stage2_rt, fmri2_stage2_rt, training_stage2_rt))

RT_no_session <- list("Stage 1" = vector(mode = "list", length = 34),
                      "Stage 2" = vector(mode = "list", length = 34))

for (x in 1:34){
    RT_no_session[["Stage 2"]][[x]] <- c(RT[["Stage 2"]][[1]][[x]], 
                                         RT[["Stage 2"]][[2]][[x]], 
                                         RT[["Stage 2"]][[3]][[x]])
    
    RT_no_session[["Stage 1"]][[x]] <- c(RT[["Stage 1"]][[1]][[x]],
                                         RT[["Stage 1"]][[2]][[x]],
                                         RT[["Stage 1"]][[3]][[x]])
}
```

Baselining and reaplacing outliers
```{r}
#replacing outliers
replace_outliers <- function(x) {
  q <- quantile(x, c(0.25, 0.75), na.rm = T)
  iqr <- IQR(x, na.rm = T)
  lower_bound <- q[1] - 1.5 * iqr
  upper_bound <- q[2] + 1.5 * iqr
  x_outliers_replaced <- x
  x_outliers_replaced[x < lower_bound | x > upper_bound] <- NaN
  return(x_outliers_replaced)
}

stage2_RT_no_session <- RT_no_session[["Stage 2"]]

no_outlier <- lapply(stage2_RT_no_session, replace_outliers)

#baselining fuction
baseline_function <- function(x,y){
  x - mean(y, na.rm = T)
}

#baseline now yes
prepped_stage2_rt <- no_outlier
outlier_stage2_rt <- stage2_RT_no_session

for (x in 1:34){
  prepped_stage2_rt[[x]] <- baseline_function(prepped_stage2_rt[[x]], prepped_stage2_rt[[x]])
  outlier_stage2_rt[[x]] <- baseline_function(stage2_RT_no_session[[x]],stage2_RT_no_session[[x]])
}
```

Outliers kept in
```{r}
performance_cost_list <- list("Stable(t) Rare(t+1) Near" =
                                vector(mode = "list", length = 34), 
                              "Stable(t) Rare(t+1) Far" = 
                                vector(mode = "list", length = 34)
                                )


transitions <- c(fmri1_transitions,fmri2_transitions,training_transitions)
reallocations <- c(fmri1_reallocataions,fmri2_reallocataions,training_reallocations)
all_trials <- c(3:179,183:359, 363:539)
 

for (i in 1:34) {
    for (x in all_trials) { 
  #t-2,t-1, or t is rare stable
  if (transitions[x-2] == 1 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x-1] == 1 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 1 && reallocations[x] == 0){
    #if t+1 is rare
    if (transitions[x+1] == 1) {
      #it is near, so combine the ones that match with that with the specific RTs
        performance_cost_list[[1]][[i]] <- c(performance_cost_list[[1]][[i]], 
                                             outlier_stage2_rt[[i]][[x+1]]) #was previously prepped_stage2_rt
      }
    }
  else 
    if (transitions[x-2] == 0 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0|
      transitions[x-1] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 0 && reallocations[x] == 0)
    {
    if (transitions[x+1] == 1) {
      #it is far, so combine the ones that match with that with the specific RTs
      performance_cost_list[[2]][[i]] <- c(performance_cost_list[[2]][[i]], 
                                                outlier_stage2_rt[[i]][[x+1]])
        }
      }
    }
}
  

#the same but for non-basedlined for easier plotting

performance_cost_listNB <- list("Stable(t) Rare(t+1) Near" =
                                vector(mode = "list", length = 34), 
                              "Stable(t) Rare(t+1) Far" = 
                                vector(mode = "list", length = 34)
                                )

for (i in 1:34) {
    for (x in all_trials) { 
  #t-2,t-1, or t is rare stable
  if (transitions[x-2] == 1 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x-1] == 1 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 1 && reallocations[x] == 0){
    #if t+1 is rare
    if (transitions[x+1] == 1) {
      #it is near, so combine the ones that match with that with the specific RTs
        performance_cost_listNB[[1]][[i]] <- c(performance_cost_listNB[[1]][[i]], 
                                             stage2_RT_no_session[[i]][[x+1]]) #was previously no_outlier
      }
    }
  else 
    if (transitions[x-2] == 0 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0|
      transitions[x-1] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 0 && reallocations[x] == 0)
    {
    if (transitions[x+1] == 1) {
      #it is far, so combine the ones that match with that with the specific RTs
      performance_cost_listNB[[2]][[i]] <- c(performance_cost_listNB[[2]][[i]], 
                                                stage2_RT_no_session[[i]][[x+1]])
        }
      }
    }
  }
```

Outliers taken out
```{r}
performance_cost_list_NO <- list("Stable(t) Rare(t+1) Near" =
                                vector(mode = "list", length = 34), 
                              "Stable(t) Rare(t+1) Far" = 
                                vector(mode = "list", length = 34)
                                )


transitions <- c(fmri1_transitions,fmri2_transitions,training_transitions)
reallocations <- c(fmri1_reallocataions,fmri2_reallocataions,training_reallocations)
all_trials <- c(3:179,183:359, 363:539)
 

for (i in 1:34) {
    for (x in all_trials) { 
  #t-2,t-1, or t is rare stable
  if (transitions[x-2] == 1 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x-1] == 1 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 1 && reallocations[x] == 0){
    #if t+1 is rare
    if (transitions[x+1] == 1) {
      #it is near, so combine the ones that match with that with the specific RTs
        performance_cost_list_NO[[1]][[i]] <- c(performance_cost_list_NO[[1]][[i]], 
                                             prepped_stage2_rt[[i]][[x+1]]) 
      }
    }
  else 
    if (transitions[x-2] == 0 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0|
      transitions[x-1] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 0 && reallocations[x] == 0)
    {
    if (transitions[x+1] == 1) {
      #it is far, so combine the ones that match with that with the specific RTs
      performance_cost_list_NO[[2]][[i]] <- c(performance_cost_list_NO[[2]][[i]], 
                                                prepped_stage2_rt[[i]][[x+1]])
        }
      }
    }
}
  

#the same but for non-basedlined for easier plotting

performance_cost_listNB_NO <- list("Stable(t) Rare(t+1) Near" =
                                vector(mode = "list", length = 34), 
                              "Stable(t) Rare(t+1) Far" = 
                                vector(mode = "list", length = 34)
                                )

for (i in 1:34) {
    for (x in all_trials) { 
  #t-2,t-1, or t is rare stable
  if (transitions[x-2] == 1 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x-1] == 1 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 1 && reallocations[x] == 0){
    #if t+1 is rare
    if (transitions[x+1] == 1) {
      #it is near, so combine the ones that match with that with the specific RTs
        performance_cost_listNB_NO[[1]][[i]] <- c(performance_cost_listNB_NO[[1]][[i]], 
                                             no_outlier[[i]][[x+1]])
      }
    }
  else 
    if (transitions[x-2] == 0 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0|
      transitions[x-1] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 0 && reallocations[x] == 0)
    {
    if (transitions[x+1] == 1) {
      #it is far, so combine the ones that match with that with the specific RTs
      performance_cost_listNB_NO[[2]][[i]] <- c(performance_cost_listNB_NO[[2]][[i]], 
                                                no_outlier[[i]][[x+1]])
        }
      }
    }
  }
```

Means and sem 
```{r}
NF_mean_NO <- performance_cost_list_NO
NF_mean <- performance_cost_list
         
for (x in 1:34){
  NF_mean_NO[["Stable(t) Rare(t+1) Near"]][[x]] <- mean(NF_mean_NO[["Stable(t) Rare(t+1) Near"]][[x]], na.rm = T)
  NF_mean_NO[["Stable(t) Rare(t+1) Far"]][[x]] <- mean(NF_mean_NO[["Stable(t) Rare(t+1) Far"]][[x]], na.rm = T)
  NF_mean[["Stable(t) Rare(t+1) Near"]][[x]] <- mean(NF_mean[["Stable(t) Rare(t+1) Near"]][[x]], na.rm = T)
  NF_mean[["Stable(t) Rare(t+1) Far"]][[x]] <- mean(NF_mean[["Stable(t) Rare(t+1) Far"]][[x]], na.rm = T)
}

sem <- function(x) {
  sd(x, na.rm = T) / sqrt(length(x[!is.na(x[])]))
}

near_SEM_NO <- c()
far_SEM_NO <- c()
near_SEM <- c()
far_SEM <- c()

for (x in 1:34){
  near_SEM_NO[x] <- c(sd(performance_cost_list_NO[[1]][[x]], na.rm =T) /        sqrt(length(performance_cost_list_NO[!is.na(performance_cost_list_NO[[1]][[x]])])))
                
  far_SEM_NO[x] <- c(sd(performance_cost_list_NO[[2]][[x]], na.rm =T) /        sqrt(length(performance_cost_list_NO[!is.na(performance_cost_list_NO[[2]][[x]])])))
  
    near_SEM[x] <- c(sd(performance_cost_list[[1]][[x]], na.rm =T) /        sqrt(length(performance_cost_list[!is.na(performance_cost_list[[1]][[x]])])))
                
  far_SEM[x] <- c(sd(performance_cost_list[[2]][[x]], na.rm =T) /        sqrt(length(performance_cost_list[!is.na(performance_cost_list[[2]][[x]])])))
}

#for NB
NF_meanNB_NO <- performance_cost_listNB_NO
NF_meanNB <- performance_cost_listNB
         
for (x in 1:34){
  NF_meanNB_NO[["Stable(t) Rare(t+1) Near"]][[x]] <- mean(NF_meanNB_NO[["Stable(t) Rare(t+1) Near"]][[x]], na.rm = T)
  NF_meanNB_NO[["Stable(t) Rare(t+1) Far"]][[x]] <- mean(NF_meanNB_NO[["Stable(t) Rare(t+1) Far"]][[x]], na.rm = T)
    NF_meanNB[["Stable(t) Rare(t+1) Near"]][[x]] <- mean(NF_meanNB[["Stable(t) Rare(t+1) Near"]][[x]], na.rm = T)
  NF_meanNB[["Stable(t) Rare(t+1) Far"]][[x]] <- mean(NF_meanNB[["Stable(t) Rare(t+1) Far"]][[x]], na.rm = T)
}

sem <- function(x) {
  sd(x, na.rm = T) / sqrt(length(x[!is.na(x[])]))
}

near_SEM_NB_NO <- c()
far_SEM_NB_NO <- c()
near_SEM_NB <- c()
far_SEM_NB <- c()

for (x in 1:34){
  near_SEM_NB_NO[x] <- c(sd(performance_cost_listNB_NO[[1]][[x]], na.rm =T) /        sqrt(length(performance_cost_listNB_NO[!is.na(performance_cost_listNB_NO[[1]][[x]])])))
                
  far_SEM_NB_NO[x] <- c(sd(performance_cost_listNB_NO[[2]][[x]], na.rm =T) /        sqrt(length(performance_cost_listNB_NO[!is.na(performance_cost_listNB_NO[[2]][[x]])])))
  
  near_SEM_NB[x] <- c(sd(performance_cost_listNB[[1]][[x]], na.rm =T) /        sqrt(length(performance_cost_listNB[!is.na(performance_cost_listNB[[1]][[x]])])))
                
  far_SEM_NB[x] <- c(sd(performance_cost_listNB[[2]][[x]], na.rm =T) /        sqrt(length(performance_cost_listNB[!is.na(performance_cost_listNB[[2]][[x]])])))
}
```

```{r}
#data frame with everything
overall_df_NO <- data.frame("Distance" = c(rep("Near",34),rep("Far",34)),
                   "Means" = as.double(c(NF_mean_NO[[1]],NF_mean_NO[[2]])),
                   "SEMs" = c(near_SEM_NO, far_SEM_NO),
                   "NB Means" = as.double(c(NF_meanNB_NO[[1]], NF_meanNB_NO[[2]])),
                   "NB SEMs" = c(near_SEM_NB_NO, far_SEM_NB_NO)
                   )

overall_df <- data.frame("Distance" = c(rep("Near",34),rep("Far",34)),
                   "Means" = as.double(c(NF_mean[[1]],NF_mean[[2]])),
                   "SEMs" = c(near_SEM, far_SEM),
                   "NB Means" = as.double(c(NF_meanNB[[1]], NF_meanNB[[2]])),
                   "NB SEMs" = c(near_SEM_NB, far_SEM_NB)
                   )
```



t test 
```{r}
#no outlier
t.test(x = as.numeric(overall_df_NO[1:34,2]),
       y = as.numeric(overall_df_NO[35:68,2]), 
       alternative = "less",
       paired = TRUE,
       var.equal = T)

#with outlier
t.test(x = as.numeric(overall_df[1:34,2]),
       y = as.numeric(overall_df[35:68,2]), 
       alternative = "less",
       paired = TRUE,
       var.equal = T)
```

plotting
```{r}
library(ggpubr)
ggbarplot(overall_df_NO, x = "Distance", y = "NB.Means",
          xlab = "Distance Since Last Rare Transition",
          ylab = "Reation Time (s)",
          title = "Near vs Far Stage 2 RT Following a Rare Transition, No Outliers",
          color = "Black",
          fill = "Distance",
          palette = "jco",
          size = .5,
          width = .5,
          add = c("mean_se"),
          add.params = list(size = .5),
          error.plot = c("errorbar")
          ) +
  geom_point(shape = 4, size = 2) +
  guides(fill = F)  + 
  geom_errorbar(aes(ymin = NB.Means - NB.SEMs, ymax = NB.Means + NB.SEMs), width = .05, position = "identity")
  

ggbarplot(overall_df, x = "Distance", y = "NB.Means",
          xlab = "Distance Since Last Rare Transition",
          ylab = "Reation Time (s)",
          title = "Near vs Far Stage 2 RT Following a Rare Transition, With Outliers",
          color = "Black",
          fill = "Distance",
          palette = "jco",
          size = .5,
          width = .5,
          add = c("mean_se"),
          add.params = list(size = .5),
          error.plot = c("errorbar")
          ) +
  geom_point(shape = 4, size = 2) +
  guides(fill = F)  + 
  geom_errorbar(aes(ymin = NB.Means - NB.SEMs, ymax = NB.Means + NB.SEMs), width = .05, position = "identity") +
  annotate("text", x = 1, y = .9, label = "***", size = 6)
  
```


## NOW WITH COMMON ON t+1 INSTEAD OF RARE

```{r}
#assigning RT to proper indices
performance_cost_list_C <- list("Stable(t) Rare(t+1) Near" =
                                vector(mode = "list", length = 34), 
                              "Stable(t) Rare(t+1) Far" = 
                                vector(mode = "list", length = 34)
                                )

for (i in 1:34) {
    for (x in all_trials) { 
  #t-2,t-1, or t is rare stable
  if (transitions[x-2] == 1 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x-1] == 1 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 1 && reallocations[x] == 0){
    #if t+1 is common
    if (transitions[x+1] == 0) {
      #it is near, so combine the ones that match with that with the specific RTs
        performance_cost_list_C[[1]][[i]] <- c(performance_cost_list_C[[1]][[i]], 
                                             prepped_stage2_rt[[i]][[x+1]])
      }
    }
  else 
    if (transitions[x-2] == 0 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0|
      transitions[x-1] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 0 && reallocations[x] == 0)
    {
    if (transitions[x+1] == 0) {
      #it is far, so combine the ones that match with that with the specific RTs
      performance_cost_list_C[[2]][[i]] <- c(performance_cost_list_C[[2]][[i]], 
                                                prepped_stage2_rt[[i]][[x+1]])
        }
      }
    }
  }

#the same but for non-basedlined for easier plotting

performance_cost_listNB_C <- list("Stable(t) Rare(t+1) Near" =
                                vector(mode = "list", length = 34), 
                              "Stable(t) Rare(t+1) Far" = 
                                vector(mode = "list", length = 34)
                                )

for (i in 1:34) {
    for (x in all_trials) { 
  #t-2,t-1, or t is rare stable
  if (transitions[x-2] == 1 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x-1] == 1 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 1 && reallocations[x] == 0){
    #if t+1 is rare
    if (transitions[x+1] == 0) {
      #it is near, so combine the ones that match with that with the specific RTs
        performance_cost_listNB_C[[1]][[i]] <- c(performance_cost_listNB_C[[1]][[i]], 
                                             no_outlier[[i]][[x+1]])
      }
    }
  else 
    if (transitions[x-2] == 0 && reallocations[x-2] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0|
      transitions[x-1] == 0 && reallocations[x-1] == 0 && reallocations[x] == 0| 
      transitions[x] == 0 && reallocations[x] == 0)
    {
    if (transitions[x+1] == 0) {
      #it is far, so combine the ones that match with that with the specific RTs
      performance_cost_listNB_C[[2]][[i]] <- c(performance_cost_listNB_C[[2]][[i]], 
                                                no_outlier[[i]][[x+1]])
        }
      }
    }
}

#taking means of the baselined
NF_mean_C <- performance_cost_list_C
         
for (x in 1:34){
  NF_mean_C[["Stable(t) Rare(t+1) Near"]][[x]] <- mean(NF_mean_C[["Stable(t) Rare(t+1) Near"]][[x]], na.rm = T)
  NF_mean_C[["Stable(t) Rare(t+1) Far"]][[x]] <- mean(NF_mean_C[["Stable(t) Rare(t+1) Far"]][[x]], na.rm = T)
}

sem <- function(x) {
  sd(x, na.rm = T) / sqrt(length(x[!is.na(x[])]))
}

near_SEM_C <- c()
far_SEM_C <- c()

for (x in 1:34){
  near_SEM_C[x] <- c(sd(performance_cost_list_C[[1]][[x]], na.rm =T) /        sqrt(length(performance_cost_list_C[!is.na(performance_cost_list_C[[1]][[x]])])))
                
  far_SEM_C[x] <- c(sd(performance_cost_list_C[[2]][[x]], na.rm =T) /        sqrt(length(performance_cost_list_C[!is.na(performance_cost_list_C[[2]][[x]])])))
}

#takng means for NB
NF_meanNB_C <- performance_cost_listNB_C
         
for (x in 1:34){
  NF_meanNB_C[["Stable(t) Rare(t+1) Near"]][[x]] <- mean(NF_meanNB_C[["Stable(t) Rare(t+1) Near"]][[x]], na.rm = T)
  NF_meanNB_C[["Stable(t) Rare(t+1) Far"]][[x]] <- mean(NF_meanNB_C[["Stable(t) Rare(t+1) Far"]][[x]], na.rm = T)
}

sem <- function(x) {
  sd(x, na.rm = T) / sqrt(length(x[!is.na(x[])]))
}

near_SEM_NB_C <- c()
far_SEM_NB_C <- c()

for (x in 1:34){
  near_SEM_NB_C[x] <- c(sd(performance_cost_listNB_C[[1]][[x]], na.rm =T) /        sqrt(length(performance_cost_listNB_C[!is.na(performance_cost_listNB_C[[1]][[x]])])))
                
  far_SEM_NB_C[x] <- c(sd(performance_cost_listNB[[2]][[x]], na.rm =T) /        sqrt(length(performance_cost_listNB_C[!is.na(performance_cost_listNB_C[[2]][[x]])])))
}

overall_df_C <- data.frame("Distance" = c(rep("Near",34),rep("Far",34)),
                   "Means" = as.double(c(NF_mean_C[[1]],NF_mean_C[[2]])),
                   "SEMs" = c(near_SEM_C, far_SEM_C),
                   "NB Means" = as.double(c(NF_meanNB_C[[1]], NF_meanNB_C[[2]])),
                   "NB SEMs" = c(near_SEM_NB_C, far_SEM_NB_C)
                   )
```

t test :)
```{r}
t.test(x = as.numeric(overall_df_C[1:34,2]),
       y = as.numeric(overall_df_C[35:68,2]),
       paired = TRUE,
       var.equal = T)
```

```{r}
library(ggpubr)
ggbarplot(overall_df_C, x = "Distance", y = "NB.Means",
          xlab = "Distance Since Last Rare Transition",
          ylab = "Reation Time (s)",
          title = "Near vs Far Stage 2 RT Following a Common Transition",
          color = "Black",
          fill = "Distance",
          palette = "jco",
          size = .5,
          width = .5,
          add = c("mean_se"),
          add.params = list(size = .5),
          error.plot = c("errorbar")
          ) +
  geom_point(shape = 4, size = 2) +
  guides(fill = F)  + 
  geom_errorbar(aes(ymin = NB.Means - NB.SEMs, ymax = NB.Means + NB.SEMs), width = .05, position = "identity") 
```
