---
title: "Logistic Regression"
author: "Ian McCarthy"
date: "2024-03-17"
output: html_document
---

```{r}
library(tidyverse)
library(rcompanion)
library(MASS)
library(huxtable)
library(cowplot)
library(corrplot)
library(MPV)
library(leaps)
library(ppcor)
library(car)
library(glmnet)
library(psych)
library(dbplyr)
```

```{r}
#fmri1 data
mat.fMRI1 <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S\\d+_fMRI1_r3_\\d+-\\d+.mat$", 
                        full.names = TRUE)

#fmri2 data
mat.fMRI2 <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S\\d+_fMRI2_r3_\\d+-\\d+.mat$", 
                        full.names = TRUE)

#training data - creates duplicates? figure out
mat.training <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S\\d+_training_r3_\\d+-\\d+.mat$", 
                        full.names = TRUE)

#S05_fmri1_r1 and s45_fmri2_r1
mat.errors <- list.files(path = "/Users/ianro/Documents/CA2Step 2024", 
                        pattern = "CA2step_S05_fMRI1_r1_\\d+-\\d+.mat$|CA2step_S45_fMRI2_r1_\\d+-\\d+.mat$|CA2step_S45_fMRI2_r2_\\d+-\\d+.mat$", 
                        full.names = TRUE)

##fmri1 loop

for (x in mat.fMRI1) {
  
  #creates file name matching the matlab file name without .mat
  file_name <- tools::file_path_sans_ext(basename(x))
  
  #convert data into r
  mat_data <- readMat(x)
  
  #assigns the file name to each individual participant in the list
  assign(file_name, mat_data)
  
  #create list of data
  
    env <- ls() #current environment
    fmri1_participants <- c(env[grep(pattern = "CA2step_S\\d+_fMRI1_r3_\\d+-\\d+$|CA2step_S09_fMRI2_r3_20230505-1347", ls())]) #take the participants matching pattern in env
    fmri1_list <- list() #empty list for loop
  
    #for everyone in the fmri1 participants, put them in a list
    for (i in fmri1_participants){
    
     fmri1_list[[i]] <- get(i)
    
      }
  
  #confirmation message
  cat("Converted and stored", x, "as", file_name, "in R environment. \n")

}

fmri1_list <- fmri1_list[-19] #get rid of s24
fmri1_list <- fmri1_list[-2]  #get rid of s01_0508 since that's actually S09_fmri2


#adding in missing data
s05_fmri1_r1 <- readMat(mat.errors[1])

fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[3]] <- s05_fmri1_r1[["data"]][[3]]
fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[4]] <- s05_fmri1_r1[["data"]][[4]]
fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[5]] <- s05_fmri1_r1[["data"]][[5]]
fmri1_list[["CA2step_S05_fMRI1_r3_20221028-1516"]][["data"]][[6]] <- s05_fmri1_r1[["data"]][[6]]



##fmri2 loop

for (x in mat.fMRI2) {
  
  #creates file name matching the matlab file name without .mat
  file_name <- tools::file_path_sans_ext(basename(x))
  
  #convert data into r
  mat_data <- readMat(x)
  
  #assigns the file name to each individual participant in the list
  assign(file_name, mat_data)
  
  #create list of data
  
    env <- ls() #current environment
    fmri2_participants <- c(env[grep(pattern = "CA2step_S\\d+_fMRI2_r3_\\d+-\\d+$|CA2step_S01_fMRI1_r3_20230508-1206",
                            ls())]) #take the participants matching pattern in env
    fmri2_list <- list() #empty list for loop
  
    #for everyone in the fmri1 participants, put them in a list
    for (i in fmri2_participants){
    
     fmri2_list[[i]] <- get(i)
    
      }
  
  #confirmation message
  cat("Converted and stored", x, "as", file_name, "in R environment. \n")

}

#take out current S09 (0505) since it's the wrong one
fmri2_list <- fmri2_list[-9]

#adding in missing data

s45_fmri2_r1 <- readMat(mat.errors[2])
s45_fmri2_r2 <- readMat(mat.errors[3])

fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[1]] <- s45_fmri2_r1[["data"]][[1]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[2]] <- s45_fmri2_r1[["data"]][[2]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[3]] <- s45_fmri2_r1[["data"]][[3]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[4]] <- s45_fmri2_r1[["data"]][[4]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[5]] <- s45_fmri2_r1[["data"]][[5]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[6]] <- s45_fmri2_r1[["data"]][[6]]
fmri2_list[["CA2step_S45_fMRI2_r3_20230427-1717"]][["data"]][[12]] #template is missing, take it from the template (check date)


##training loop

for (x in mat.training) {
  
  #creates file name matching the matlab file name without .mat
  file_name <- tools::file_path_sans_ext(basename(x))
  
  #convert data into r
  mat_data <- readMat(x)
  
  #assigns the file name to each individual participant in the list
  assign(file_name, mat_data)
  
  #create list of data
  
  env <- ls() #current environment
  training_participants <- env[grep(pattern = "CA2step_S\\d+_training_r3_\\d+-\\d+$", ls())] #take the participants matching pattern in env
  training_list <- list() #empty list for loop
  
  #for everyone in the fmri1 participants, put them in a list
  for (i in training_participants){
    
    training_list[[i]] <- get(i)
    
  }
  
  #taking out all duplicates and bad ones
  
  training_error <- c(-45, -43, -40, -37, -36, -28, -27, -25, -23, -22, -19, -18, -2, -3, -4, -7, -23, -31)
  
  for (z in training_error) {
    
    training_list <- training_list[z]
  }
  
  #confirmation message
  cat("Converted and stored", x, "as", file_name, "in R environment. \n")
  
}

all_data <- list("fmri 1" = fmri1_list,
                 "fmri 2" = fmri2_list,
                 "training" = training_list)

new_elements <- list("CA2step_S09_fMRI2_r3" = c(1),
                     "CA2step_S17_fMRI2_r3" = c(1),
                     "CA2step_S18_fMRI2_r3" = c(1))
all_data[[2]] <-  append(all_data[[2]],new_elements)

order <- c(1,2,3,4,5,6,7,8,32,9,10,11,12,33,34,13,14:31)
testing. <- all_data[[2]]
testing.ordered <- testing.[order]

all_data[[2]] <- testing.ordered

training_transitions <- all_data[["training"]][["CA2step_S01_training_r3_20221021-1222"]][["expe"]][[1]][[5]]
training_reallocations <- all_data[["training"]][["CA2step_S01_training_r3_20221021-1222"]][["expe"]][[1]][[6]]
fmri1_transitions <- `CA2step_S01_fMRI1_r3_20230316-1704`[["expe"]][[1]][[5]]
fmri1_reallocataions <- `CA2step_S01_fMRI1_r3_20230316-1704`[["expe"]][[1]][[6]]
fmri2_transitions <- `CA2step_S02_fMRI2_r3_20230509-1300`[["expe"]][[1]][[5]]
fmri2_reallocataions <- `CA2step_S02_fMRI2_r3_20230509-1300`[["expe"]][[1]][[6]]
```


```{r}
#getting rewards per participant
fmri1_rew <- matrix(nrow = 34, ncol = 180)
fmri2_rew <- matrix(nrow = 34, ncol = 180)
training_rew <- matrix(nrow = 34, ncol = 180)

#replacing missing data, the replacement already has NaNs
all_data[["training"]][["CA2step_S43_training_r3_20230825-1419"]][["data"]][[4]] <- all_data[["training"]][["CA2step_S43_training_r3_20230825-1419"]][["data"]][[3]]

  for (i in 1:34){
    fmri1_rew[i,] <- c(all_data[[1]][[i]][[1]][[6]][[5]],
                       all_data[[1]][[i]][[1]][[12]][[5]],
                       all_data[[1]][[i]][[1]][[18]][[5]])
  
    training_rew[i,] <- c(all_data[[3]][[i]][[1]][[4]][[5]],
                          all_data[[3]][[i]][[1]][[8]][[5]],
                          all_data[[3]][[i]][[1]][[12]][[5]])
  }

subs <- c(2:8,10:13,16:31,33,34)
  for (i in subs){
    fmri2_rew[i,] <- c(all_data[[2]][[i]][[1]][[6]][[5]],
                       all_data[[2]][[i]][[1]][[12]][[5]],
                       all_data[[2]][[i]][[1]][[18]][[5]])
  }

#subbing in data for s45 since it's stored differently
fmri2_rew[32,] <- c(all_data[[2]][[i]][[1]][[6]][[5]],
                       all_data[[2]][[i]][[1]][[11]][[5]],
                       all_data[[2]][[i]][[1]][[17]][[5]])
fmri2_rew[9,] <- c(all_data[["fmri 2"]][["CA2step_S01_fMRI1_r3_20230508-1206"]][["data"]][[6]][[5]],
                   all_data[["fmri 2"]][["CA2step_S01_fMRI1_r3_20230508-1206"]][["data"]][[12]][[5]],
                   all_data[["fmri 2"]][["CA2step_S01_fMRI1_r3_20230508-1206"]][["data"]][[18]][[5]])
```

Plan:
1. Structure data to where each participant has a 179x3 matrix
  y  One column is switch or stay on t
   x1 One column is token received on t-1
  x2(categorical)  One column is transition on t-1
    
  ARE THEY AIMING FOR SAME DESTINATION (this = switch or stay)
    For every stimulus, what destination are they aiming for, on two consecutive trials, did they repeat the same choice?
    Have to pair stimulus with the destination that it corersponds to (since stim alone doesn't tell you where)
      
  in expre/struct/stim, 1x4
     Frist 2 columns is first pair, second 2 is second pair
     First in each pair goes to first destination, second destination for second in each pair

Now everybody
```{r}
fmri1_stims <- matrix(nrow = 34, ncol = 4)
fmri2_stims <- matrix(nrow = 34, ncol = 4)
training_stims <- matrix(nrow = 34, ncol = 4)

fmri1_bg <- matrix(nrow = 34, ncol = 2)
fmri2_bg <- matrix(nrow = 34, ncol = 2)
training_bg <- matrix(nrow = 34, ncol = 2)

fmri1_choices <- matrix(nrow = 34, ncol = 180)
fmri2_choices <- matrix(nrow = 34, ncol = 180)
training_choices <- matrix(nrow = 34, ncol = 180)

for (x in 1:34){
  fmri1_stims[x,] <- all_data[[1]][[x]][[2]][[2]][[1]][[1]]
  fmri1_bg[x,] <- all_data[[1]][[x]][[2]][[2]][[2]]
  fmri1_choices[x,] <- c(all_data[[1]][[x]][[1]][[5]][[2]],
                         all_data[[1]][[x]][[1]][[11]][[2]],
                         all_data[[1]][[x]][[1]][[17]][[2]])
}

training_subs <- c(1:8,10,11,13:26,29:34)
for (x in training_subs){
  training_stims[x,] <- all_data[[3]][[x]][[2]][[2]][[1]][[1]]
  training_bg[x,] <- all_data[[3]][[x]][[2]][[2]][[2]]
  training_choices[x,] <- c(all_data[[3]][[x]][[1]][[3]][[2]],
                            all_data[[3]][[x]][[1]][[7]][[2]],
                            all_data[[3]][[x]][[1]][[11]][[2]])
}

#fixing weird participants
all_data[["training"]][["CA2step_S09_training_r3_20221103-1201"]][["expe"]] <- `CA2step_S09_training_r3_20221103-1201`[["expe"]]
training_stims[9,] <- all_data[["training"]][["CA2step_S09_training_r3_20221103-1201"]][["expe"]][[2]][[1]][[1]]
training_bg[9,] <- all_data[[3]][[9]][[1]][[2]][[2]]
training_choices[9,] <- c(all_data[[3]][[9]][[2]][[3]][[2]],
                            all_data[[3]][[9]][[2]][[7]][[2]],
                            all_data[[3]][[9]][[2]][[11]][[2]])
all_data[["training"]][["CA2step_S13_training_r3_20221117-1218"]][["expe"]] <- `CA2step_S09_training_r3_20221103-1201`[["expe"]]
training_stims[12,] <- all_data[["training"]][[12]][["expe"]][[2]][[1]][[1]]
training_bg[12,] <- all_data[[3]][[12]][[1]][[2]][[2]]
training_choices[12,] <- c(all_data[[3]][[12]][[2]][[3]][[2]],
                            all_data[[3]][[12]][[2]][[7]][[2]],
                            all_data[[3]][[12]][[2]][[11]][[2]])
all_data[["training"]][["CA2step_S37_training_r3_20230307-1739"]][["expe"]] <- `CA2step_S37_training_r3_20230307-1739`[["expe"]]
training_stims[27,] <- all_data[["training"]][[27]][["expe"]][[2]][[1]][[1]]
training_bg[27,] <- all_data[[3]][[27]][[1]][[2]][[2]]
training_choices[27,] <- c(all_data[[3]][[27]][[2]][[3]][[2]],
                            all_data[[3]][[27]][[2]][[7]][[2]],
                            all_data[[3]][[27]][[2]][[11]][[2]])
all_data[["training"]][["CA2step_S39_training_r3_20230228-1646"]][["expe"]] <- `CA2step_S39_training_r3_20230228-1646`[["expe"]]
training_stims[28,] <- all_data[["training"]][[28]][["expe"]][[2]][[1]][[1]]
training_bg[28,] <- all_data[[3]][[28]][[1]][[2]][[2]]
training_choices[28,] <- c(all_data[[3]][[28]][[2]][[3]][[2]],
                            all_data[[3]][[28]][[2]][[7]][[2]],
                            all_data[[3]][[28]][[2]][[11]][[2]])

subs <- c(2:8,10:13,16:31,33,34)
for (x in subs){
  fmri2_stims[x,] <- all_data[[2]][[x]][[2]][[2]][[1]][[1]]
  fmri2_bg[x,] <- all_data[[2]][[x]][[2]][[2]][[2]]
  fmri2_choices[x,] <- c(all_data[[2]][[x]][[1]][[5]][[2]],
                     all_data[[2]][[x]][[1]][[11]][[2]],
                     all_data[[2]][[x]][[1]][[17]][[2]])
}
#stored differently so inputing directly
fmri2_choices[32,] <- c(all_data[[2]][[32]][[1]][[5]][[2]],
                     all_data[[2]][[32]][[1]][[10]][[2]],
                     all_data[[2]][[32]][[1]][[16]][[2]])
fmri2_stims[32,] <- all_data[["fmri 2"]][["CA2step_S45_fMRI2_r3_20230427-1717"]][["expe"]][[2]][[1]][[1]]
fmri2_bg[32,] <-  all_data[["fmri 2"]][["CA2step_S45_fMRI2_r3_20230427-1717"]][["expe"]][[2]][[2]]

fmri2_stims[9,] <- all_data[[2]][[1]][[2]][[2]][[1]][[1]]
fmri2_bg[9,] <- all_data[[2]][[1]][[2]][[2]][[2]]
fmri2_choices[9,] <- c(all_data[[2]][[1]][[1]][[5]][[2]],
                     all_data[[2]][[1]][[1]][[11]][[2]],
                     all_data[[2]][[1]][[1]][[17]][[2]])
  
fmri1_rew
fmri2_rew
training_rew

fmri1_loc_choices <- fmri1_choices
fmri2_loc_choices <- fmri2_choices
training_loc_choices <- training_choices
```

Now pairing choice with locations
```{r}
#filling missing values in fmri2 with 10 so then it still loops but doesn't get included
miss <- c(1,14,15)
fmri2_choices[miss,] <- rep(10, 180)
fmri2_stims[miss,] <- rep(10, 4)
fmri2_bg[miss,] <- rep(10,2)

#pairing choice with the proper stimuli in order to properly assign the location that each choice leads to
for (i in 1:34){
  for (x in 1:180){
    if (fmri1_choices[i,x] == fmri1_stims[i,1] | fmri1_choices[i,x] == fmri1_stims[i,3]){
      fmri1_loc_choices[i,x] <- fmri1_bg[i,1]
    }
    else if (fmri1_choices[i,x] == fmri1_stims[i,2] | fmri1_choices[i,x] == fmri1_stims[i,4]){
      fmri1_loc_choices[i,x] <- fmri1_bg[i,2]
    }
    if (fmri2_choices[i,x] == fmri2_stims[i,1] | fmri2_choices[i,x] == fmri2_stims[i,3]){
      fmri2_loc_choices[i,x] <- fmri2_bg[i,1]
    }
    else if (fmri2_choices[i,x] == fmri2_stims[i,2] | fmri2_choices[i,x] == fmri2_stims[i,4]){
      fmri2_loc_choices[i,x] <- fmri2_bg[i,2]
    }
    if (training_choices[i,x] == training_stims[i,1] | training_choices[i,x] == training_stims[i,3]){
      training_loc_choices[i,x] <- training_bg[i,1]
    }
    else if (training_choices[i,x] == training_stims[i,2] | training_choices[i,x] == training_stims[i,4]){
      training_loc_choices[i,x] <- training_bg[i,2]
    }
}
}

#labeling switch or stay
fmri1_repeat <- matrix(nrow = 34, ncol = 180)
fmri2_repeat <- matrix(nrow = 34, ncol = 180)
training_repeat <- matrix(nrow = 34, ncol = 180)

for(i in 1:34){
  for (x in 2:180){
    if (fmri1_loc_choices[i,x] == fmri1_loc_choices[i,x-1]){
      fmri1_repeat[i,x] <- 0 #stay
    }
    else if (fmri1_loc_choices[i,x] != fmri1_loc_choices[i,x-1]){
      fmri1_repeat[i,x] <- 1 #switch
    } 
    if (fmri2_loc_choices[i,x] == fmri2_loc_choices[i,x-1]){
      fmri2_repeat[i,x] <- 0 #stay
    }
    else if (fmri2_loc_choices[i,x] != fmri2_loc_choices[i,x-1]){
      fmri2_repeat[i,x] <- 1 #switch
    } 
    if (training_loc_choices[i,x] == training_loc_choices[i,x-1]){
      training_repeat[i,x] <- 0 #stay
    }
    else if (training_loc_choices[i,x] != training_loc_choices[i,x-1]){
      training_repeat[i,x] <- 1 #switch
      } 
}
}
#removing first column because the first trial is not a switch or stay
training_repeat <- training_repeat[,-1]
fmri1_repeat <- fmri1_repeat[,-1]
fmri2_repeat <- fmri2_repeat[,-1]

#creating big list of each session's data per participant
log_list <- list("Tr" = vector("list", 34),
                 "Tr Com" = vector("list", 34),
                 "Tr Rare" = vector("list", 34),
                 "fmri1" = vector("list", 34),
                 "fmri1 Com" = vector("list", 34),
                 "fmri1 Rare" = vector("list", 34),
                 "fmri2" = vector("list", 34),
                 "fmri2 Com" = vector("list", 34),
                 "fmri2 Rare" = vector("list", 34)
                 )

for (i in 1:34){
  train <- data.frame("y" = c(training_repeat[i,]),
                   "x1" = c(training_rew[i,1:179]),
                   "x2" = c(training_transitions[1:179]))
  log_list[[1]][[i]] <- train
  
  firm1 <- data.frame("y" = c(fmri1_repeat[i,]),
                   "x1" = c(fmri1_rew[i,1:179]),
                   "x2" = c(fmri1_transitions[1:179]))
  log_list[[4]][[i]] <- firm1
    
  firm2 <- data.frame("y" = c(fmri2_repeat[i,]),
                   "x1" = c(fmri2_rew[i,1:179]),
                   "x2" = c(fmri2_transitions[1:179]))
  log_list[[7]][[i]] <- firm2
}

#splitting common and rare
for (i in 1:34){
  tr_com <- c(which(log_list[[1]][[i]][[3]] == 0))
  tr_rar <- c(which(log_list[[1]][[i]][[3]] == 1))
  log_list[[2]][[i]] <- log_list[[1]][[i]][tr_com,1:2]
  log_list[[3]][[i]] <- log_list[[1]][[i]][tr_rar,1:2]
  
  f1_com <- c(which(log_list[[4]][[i]][[3]] == 0))
  f1_rar <- c(which(log_list[[4]][[i]][[3]] == 1))
  log_list[[5]][[i]] <- log_list[[4]][[i]][f1_com,1:2]
  log_list[[6]][[i]] <- log_list[[4]][[i]][f1_rar,1:2]
  
  f2_com <- c(which(log_list[[7]][[i]][[3]] == 0))
  f2_rar <- c(which(log_list[[7]][[i]][[3]] == 1))
  log_list[[8]][[i]] <- log_list[[7]][[i]][f2_com,1:2]
  log_list[[9]][[i]] <- log_list[[7]][[i]][f2_rar,1:2]
}

#removing in NaN for missing data, 
fix_30 <- as.double(c(which(log_list[[2]][[30]][[2]] == 0)))
fix_30r <- as.double(c(which(log_list[[3]][[30]][[2]] == 0)))
log_list[[2]][[30]] <- log_list[[2]][[30]][-fix_30,] 
log_list[[3]][[30]] <- log_list[[3]][[30]][-fix_30r,]



model_list <- list("TR Common" = vector("list", 34),
                   "TR Rare" = vector("list", 34),
                   "F1 Common" = vector("list", 34),
                   "F1 Rare" = vector("list", 34),
                   "F2 Common" = vector("list", 34),
                   "F2 Rare" = vector("list", 34)
                   )

#creating all of the models (6 in total per participant, 2 per session, one for common trials and one for rare)
for (i in 1:34){
  
  tr_com_model <- glm(y ~ ., data = log_list[[2]][[i]], family = binomial)
  model_list[[1]][[i]] <- tr_com_model
  
  tr_rar_model <- glm(y ~ ., data = log_list[[3]][[i]], family = binomial)
  model_list[[2]][[i]] <- tr_rar_model
  
  f1_com_model <- glm(y ~ ., data = log_list[[5]][[i]], family = binomial)
  model_list[[3]][[i]] <- f1_com_model
  
  f1_rar_model <- glm(y ~ ., data = log_list[[6]][[i]], family = binomial)
  model_list[[4]][[i]] <- f1_rar_model
}

#creating all the models for fmri2 since there are fewer participants
omit2 <- c(2:13,16:34)
for (i in omit2){  
  f2_com_model <- glm(y ~ ., data = log_list[[8]][[i]], family = binomial)
  model_list[[5]][[i]] <- f2_com_model

  f2_rar_model <- glm(y ~ ., data = log_list[[9]][[i]], family = binomial)
  model_list[[6]][[i]] <- f2_rar_model
}

#creating matrix of all the betas, with the first column being common trial betas and the second columns being rare trial betas
beta_matrix <- matrix(nrow = 34, ncol = 2)
b0_matrix <- matrix(nrow = 34, ncol = 2)
for (i in 1:34){
  com_beta_avg <-  mean(c(model_list[[1]][[i]][["coefficients"]][[2]],
                          model_list[[3]][[i]][["coefficients"]][[2]],
                          model_list[[5]][[i]][["coefficients"]][[2]]))
  rar_beta_avg <-  mean(c(model_list[[2]][[i]][["coefficients"]][[2]],
                          model_list[[4]][[i]][["coefficients"]][[2]],
                          model_list[[6]][[i]][["coefficients"]][[2]]))
  beta_matrix[i,1] <- com_beta_avg
  beta_matrix[i,2] <- rar_beta_avg
}
for (i in 1:34){
  #b0 one is for the plotting
  com_b0_avg <-  mean(c(model_list[[1]][[i]][["coefficients"]][[1]],
                          model_list[[3]][[i]][["coefficients"]][[1]],
                          model_list[[5]][[i]][["coefficients"]][[1]]))
  rar_b0_avg <-  mean(c(model_list[[2]][[i]][["coefficients"]][[1]],
                          model_list[[4]][[i]][["coefficients"]][[1]],
                          model_list[[6]][[i]][["coefficients"]][[1]]))
  b0_matrix[i,1] <- com_b0_avg
  b0_matrix[i,2] <- rar_b0_avg
}
combined_rare_beta <- mean(beta_matrix[,2])
combined_com_beta <- mean(beta_matrix[,1])

combined_rare_b0 <- mean(b0_matrix[,2])
combined_com_b0 <- mean(b0_matrix[,1])

#testing if the betas are different than 0
t.test(beta_matrix[,2], alternative = "greater")
t.test(beta_matrix[,1], alternative = "less")
```
Now plotting
```{r}
# Define the logistic function


logistic <- function(x, x0, x1) {
  return(1 / (1 + exp(-(x0 + x1*x))))
}

avg_common <- logistic(c(log_list[["Tr Com"]][[1]][["x1"]],
                     log_list[["fmri1 Com"]][[1]][["x1"]],
                     log_list[["fmri2 Com"]][[1]][["x1"]]),
                          combined_com_b0,
                          combined_com_beta)

avg_rare <- logistic(c(log_list[["Tr Rare"]][[1]][["x1"]],
                     log_list[["fmri1 Rare"]][[1]][["x1"]],
                     log_list[["fmri2 Rare"]][[1]][["x1"]]),
                          combined_rare_b0,
                          combined_rare_beta)

#this is using the overall averaged beta across all participants
plot(x = c(log_list[["Tr Com"]][[1]][["x1"]],
                     log_list[["fmri1 Com"]][[1]][["x1"]],
                     log_list[["fmri2 Com"]][[1]][["x1"]]), 
     y = avg_common,
     type = "n", 
     lwd = 2,
     xlab = "Reward (t-1)", ylab = "Switch Probability (t)", main = "Switch or Stay, Common Trials",
     xaxt = "n",
     bg = "lightgray")
axis(1, at = seq(min(1), max(4), by = 1))
abline(h = 0.5, col = "black", lty = 2)
box()
points(x = c(log_list[["Tr Com"]][[1]][["x1"]],
                     log_list[["fmri1 Com"]][[1]][["x1"]],
                     log_list[["fmri2 Com"]][[1]][["x1"]]), 
     y = avg_common,
     pch = 16)

x_vals <- c(log_list[["Tr Com"]][[1]][["x1"]],
                     log_list[["fmri1 Com"]][[1]][["x1"]],
                     log_list[["fmri2 Com"]][[1]][["x1"]])
lines(x = x_vals[order(x_vals, decreasing = T)], 
     y = avg_common[order(avg_common)],
     col = "red", 
     lwd = 4)

#this is using the betas per participant
for (x in 1:34) {
  
  x_loop_vals <- c(log_list[["Tr Com"]][[x]][["x1"]],
                     log_list[["fmri1 Com"]][[x]][["x1"]],
                     log_list[["fmri2 Com"]][[x]][["x1"]])
  
  y_loop_vals <- logistic(x_loop_vals,
                          b0_matrix[x,1],
                          beta_matrix[x,1])
  
  lines(x  = x_loop_vals[order(x_loop_vals, decreasing = T)],
        y = y_loop_vals[order(y_loop_vals)],
  col = "grey",
  lwd = 1,
  pch = 16)
}
legend("topright", legend = c("Average", "Individual"), col = c("red", "grey"), lty = 1:1)
#this is using the overall averaged beta across all participants
plot(x = c(log_list[["Tr Rare"]][[1]][["x1"]],
                     log_list[["fmri1 Rare"]][[1]][["x1"]],
                     log_list[["fmri2 Rare"]][[1]][["x1"]]), 
     y = avg_rare,
     type = "n", 
     lwd = 2,
     xlab = "Reward (t-1)", ylab = "Switch Probability (t)", main = "Switch or Stay, Rare Trials",
     xaxt = "n",
     bg = "lightgray")
axis(1, at = seq(min(1), max(4), by = 1))
abline(h = 0.5, col = "black", lty = 2)
box()
points(x = c(log_list[["Tr Rare"]][[1]][["x1"]],
                     log_list[["fmri1 Rare"]][[1]][["x1"]],
                     log_list[["fmri2 Rare"]][[1]][["x1"]]), 
     y = avg_rare,
     pch = 16)
rare_x_vals <- c(log_list[["Tr Rare"]][[1]][["x1"]],
                     log_list[["fmri1 Rare"]][[1]][["x1"]],
                     log_list[["fmri2 Rare"]][[1]][["x1"]])
lines(x = rare_x_vals[order(rare_x_vals, decreasing = T)], 
     y = avg_rare[order(avg_rare, decreasing = T)],
     col = "red", 
     lwd = 4)

#this is using the betas per participant
for (x in 1:34) {
  rare_x_loop_vals <- c(log_list[["Tr Rare"]][[x]][["x1"]],
                     log_list[["fmri1 Rare"]][[x]][["x1"]],
                     log_list[["fmri2 Rare"]][[x]][["x1"]])
  rare_y_loop_vals <- logistic(c(log_list[["Tr Rare"]][[x]][["x1"]],
                     log_list[["fmri1 Rare"]][[x]][["x1"]],
                     log_list[["fmri2 Rare"]][[x]][["x1"]]),
                     b0_matrix[x,2],
                    beta_matrix[x,2])
  lines(x  = rare_x_loop_vals[order(rare_x_loop_vals, decreasing = T)],
        y = rare_y_loop_vals[order(rare_y_loop_vals, decreasing = T)],
        col = "grey",
        lwd = 1,
        pch = 16)
}
legend("topleft", legend = c("Average", "Individual"), col = c("red", "grey"), lty = 1:1)
```



Perfect learner plan:
How would each response/curve look like for a perfect learner
- Distance between perfect and subject curve to give stage 1 CA

Stage 2 idea:
Token will greatly predict choice on stage two whether it's stable or reallocation
But after a reallocation, if they get a low value coin, there will be an exploratory trial where the choice is random

If it's not the same destination (common) following a reallocation, the choice will be random in the alternate destination
So stage 2 choice will be predicted by coin, trial type
predictors: t transition, and token t-1


STAGE 2 MODEL:

predicting choice at stage 2
dependent on token on t-1
transition on trial t-1 
- can remove this by switching  simplified high and low
transition on t


Then for more complexity (adding interactions of last time been in that destination) check screenshot (google sheets that lindsay made)


Possible logistic for stage 2:

Stay or switch based on how many trials ago you've been at that destination
y1 stage 2 choice = token t-1, transition t-1, transition t
y1 stage 2 choice = token t-2, transition t-2, transition t
y1 stage 2 choice = token t-3, transition t-3, transition t


