---
title: "Final"
author: "Ian McCarthy"
date: "2024-03-12"
output: html_document
---

```{r}
library(tidyverse)
library(rcompanion)
library(MASS)
library(huxtable)
library(cowplot)
library(corrplot)
library(MPV)
library(leaps)
library(ppcor)
library(car)
library(glmnet)
library(psych)
library(rcompanion) #To load in the library needed
library(dbplyr)
wine <- read.csv("winequality-red.csv", header = T,  sep =";") #model wine quality
```
So in all these plots, tend to be two clusters that determine lower vs higher quality for the fitted values


Relationships from graphs:
- Fixed acidity: Not much change with increasing
- volatile acidity: With increase comes decrease in quality
- Citric acid: Not much change
- Residual Sugar: Not much change
- Chlorides: Not much change
- Free Sulfur Dioxide: not much change
- Total Sulfur Dioxide: Lower has more 8s, but seems pretty evenly distributed
- Density: more variability, but .999 tends to produce 5-7
- pH: pretty much the same
- Sulphates: slight increase in quality with increase
- Alcohol: slight increase in quality with increase


```{r}
wine_model <- lm(quality ~ ., data = wine)

ggplot(data = wine, mapping = aes(x = wine$fixed.acidity, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm") + 
  labs(title = "Quality and Fixed Acidity") + 
  ylab("Quality") + 
  xlab("Fixed Acidity")


ggplot(data = wine, mapping = aes(x = wine$volatile.acidity, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Volatile Acidity") + 
  ylab("Quality") + 
  xlab("Volatile Acidity")

ggplot(data = wine, mapping = aes(x = wine$citric.acid, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Citric Acid") + 
  ylab("Quality") + 
  xlab("Citric Acid")

ggplot(data = wine, mapping = aes(x = wine$residual.sugar, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Residual Sugar") + 
  ylab("Quality") + 
  xlab("Residual Sugar")

ggplot(data = wine, mapping = aes(x = wine$chlorides, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Chlorides") + 
  ylab("Quality") + 
  xlab("Chlorides")

ggplot(data = wine, mapping = aes(x = wine$free.sulfur.dioxide, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Free Sulfur Dioxide") + 
  ylab("Quality") + 
  xlab("Free Sulfur Dioxide")

ggplot(data = wine, mapping = aes(x = wine$total.sulfur.dioxide, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Total Sulfur Dioxide") + 
  ylab("Quality") + 
  xlab("Total Sulfur Dioxide")

ggplot(data = wine, mapping = aes(x = wine$density, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Density") + 
  ylab("Quality") + 
  xlab("Density")

ggplot(data = wine, mapping = aes(x = wine$pH, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and pH") + 
  ylab("Quality") + 
  xlab("pH")

ggplot(data = wine, mapping = aes(x = wine$sulphates, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Sulphates") + 
  ylab("Quality") + 
  xlab("Sulphates")

ggplot(data = wine, mapping = aes(x = wine$alcohol, y = wine$quality)) +
  geom_point() + 
  #geom_smooth(method = "lm")+ 
  labs(title = "Quality and Alcohol") + 
  ylab("Quality") + 
  xlab("Alcohol")

hist(winex$x6, main = "Free Sulfur Dioxide Histogram", xlab = "Free Sulfur Dioxide", col = "blue")
hist(winex$x7, main = "Total Sulfur Dioxide Histogram", xlab = "Total Sulfur Dioxide", col = "blue")
hist(log(winex$x6), main = "Log Free Sulfur Dioxide Histogram", xlab = "Log(Free Sulfur Dioxide)", col = "orange")
hist(log(winex$x7), main = "Log Total Sulfur Dioxide Histogram", xlab = "Log(Total Sulfur Dioxide)", col = "orange")
```

Correlations WHY NANS
Correlations:
- Fixed acitiy strongly negatively correlated with pH
- Fixed acidity strongly positively correalted with citric acid and density
- Volatile acidity and citric acid moderately negatively correlated
- Citric acid and pH moderately negatively correlated
- Alcohol and density moderately negatively correlated
```{r}
datamatrix <- cor(wine[,1:11])
corrplot(datamatrix,method = "number")
pcor(datamatrix,method = "pearson")$p.value
```

Testing assumptions - neither normality nor heterscedasticity is met
```{r}
qqnorm(wine_model$residuals)
shapiro.test(wine_model$residuals)

Group = rep("Lower",nrow(wine)) #Creates a vector that repeats "Lower" n times
Group[wine$quality > median(wine$quality)] = "Upper" #Changing the appropriate values to "Upper"
Group = as.factor(Group) #Changes it to a factor, which R recognizes as a grouping variable.
wine$Group = Group
the.FKtest= fligner.test(wine_model$residuals, wine$Group)
the.FKtest

```

Trying a box cox - normality is bad but heteroscedasticity is good
```{r}
BC = boxcox(wine_model,lambda = seq(-6,6,0.1),plotit = FALSE)
lambda = BC$x[which.max(BC$y)]
lambda
BC.Y = (wine$quality^lambda - 1)/lambda
BC.data = data.frame(Y = BC.Y)
BC.data[,2:12] <- wine[,1:11]
# created a new data set with my new Y and my original X1
par(mfrow = c(1,2))
BC.model = lm(Y ~ ., data = BC.data)
plot(BC.model$residuals)
qqnorm(BC.model$residuals)
qqline(BC.model$residuals)


Group = rep("Lower",nrow(wine)) #Creates a vector that repeats "Lower" n times
Group[BC.data$Y > median(BC.data$Y)] = "Upper" #Changing the appropriate values to "Upper"
Group = as.factor(Group) #Changes it to a factor, which R recognizes as a grouping variable.
BC.data$Group = Group

fligner.test(BC.model$residuals, BC.data$Group)
shapiro.test(BC.model$residuals)
plot(BC.model$fitted.values,BC.model$residuals)
```

Trying some model selection stuff - FB BIC - didn't pass assumptions
```{r}
winex <- wine
winex <- winex[,-13]
colnames(winex) <- c("x1","x2","x3","x4","x5","x6","x7","x8","x9","x10","x11","y")
formulas = map(1:11, ~ combn(paste0("x",1:11), .x) %>% 
      apply(., 2, function(v) paste0("y ~ ", paste(v, collapse=" + ")))) %>% 
  unlist

FB.model.BIC = stepAIC(empty_model,  scope = list(lower = empty_model, upper= full_model), k = log(nrow(winex)),trace=FALSE,direction = "both")
FB.model.BIC

shapiro.test(FB.model.BIC$residuals)
fligner.test(FB.model.BIC$residuals, wine$Group)
plot(FB.model.BIC$fitted.values, FB.model.BIC$residuals)
```

Removing outliers for FB model
```{r}
ei.s = FB.model.BIC$residuals/sqrt(sum(FB.model.BIC$residuals^2)/(nrow(winex) - length(FB.model.BIC$coefficients)))
ri = rstandard(FB.model.BIC)
ti = rstudent(FB.model.BIC)

alpha = 0.1 ; n = nrow(winex); p = length(FB.model.BIC$coefficients)
cutoff = qt(1-alpha/(2*n), n -p )
cutoff.deleted = qt(1-alpha/(2*n), n -p -1 )

outliers = which(abs(ei.s)> cutoff | abs(ri) > cutoff | abs(ti) > cutoff.deleted)
wine[outliers,]

#now leverage
all.values = influence.measures(FB.model.BIC)$infmat
lev.hat = which(all.values[,"hat"] >2*p/n)
lev.DF = which(all.values[,"dffit"] >1)
lev.D = which(all.values[,"cook.d"] >qf(0.50,p,n-p))
winex[lev.hat,]
winex[lev.DF,] #nothing
winex[lev.D,]#nothing

#leverage point plus outliers
wine[outliers,]
wine[lev.hat,]
OL <- c(14,16,18,20,39,43,44,46,80,82,833)
wine_NOL <- wine[-OL,]

Group = rep("Lower",nrow(wine_NOL)) #Creates a vector that repeats "Lower" n times
Group[wine_NOL$quality > median(wine_NOL$quality)] = "Upper" #Changing the appropriate values to "Upper"
Group = as.factor(Group) #Changes it to a factor, which R recognizes as a grouping variable.
wine_NOL$Group = Group
```

Is this valid to rerun the stuff but without the outlier/lp. 
It validates assumptions better than original but still not good... so do transform or alternate thing?
```{r}
winex2 <- wine_NOL
winex2 <- winex2[,-13]
colnames(winex2) <- c("x1","x2","x3","x4","x5","x6","x7","x8","x9","x10","x11","y")
full_model2 <- lm(y~., data = winex2)
empty_model2 <- lm(y~1, data = winex2)
FB.model.BIC2 = stepAIC(empty_model2,  scope = list(lower = empty_model2, upper= full_model2), k = log(nrow(winex2)),trace=FALSE,direction = "both")

shapiro.test(FB.model.BIC2$residuals)
fligner.test(FB.model.BIC2$residuals, wine_NOL$Group)
plot(FB.model.BIC2$fitted.values, FB.model.BIC2$residuals)
```


Trying colinearity stuff - ph and fixed acidity too high
Try colinearity stuff. Can I use colinearity after something like BIC? What can I gleam off the graphs?
So how do fix? binomial?

```{r}
vif(full_model) 
vm <- lm(y ~ x1*x3+x1*x8+x1*x9+x2*x3+x3*x9+x8*x11+x2+x4+x5+x6+x7+x10, data = winex)
shapiro.test(vm$residuals)
fm <- lm(y~x2+x4+x5+x6+x7+x10, data = winex)

before = stepAIC(empty_model,  scope = list(lower = empty_model, upper= fm), k = log(nrow(winex)),trace=FALSE,direction = "both")

shapiro.test(before$residuals)
fligner.test(before$residuals, wine$Group)

before_vec <- before$fitted.values
before_vec[aa] <- floor(before_vec[aa])
before_vec[bb] <- ceiling(before_vec[bb])
before_vec[cc] <- floor(before_vec[cc])
before_vec[dd] <- ceiling(before_vec[dd])
before_vec[ee] <- floor(before_vec[ee])
before_vec[ff] <- ceiling(before_vec[ff])
before_vec[gg] <- floor(before_vec[gg])
before_vec[hh] <- ceiling(before_vec[hh])
before_vec[ii] <- floor(before_vec[ii])
before_vec[jj] <- ceiling(before_vec[jj])
before_vec_residuals <- wine$quality - before_vec
shapiro.test(before_vec_residuals)
fligner.test(before_vec_residuals, wine$Group)
```

Lasso regression since want correct model - good xs are x2,x3,(x4 or x5),x10 so does that mean that's the model? What are the Bs?
```{r}
set.seed(123)
y <- winex %>% dplyr::select(y) %>% scale(center = TRUE, scale = FALSE) %>% as.matrix()
X <- winex %>% dplyr::select(-y) %>% as.matrix()
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)


lasso_cv <- cv.glmnet(X, y, alpha = 1, lambda = lambdas_to_try,
                      standardize = TRUE, nfolds = 10)
plot(lasso_cv)
grid = 10^seq(1, -2, length = 100)
lasso_cv$lambda.min

lasso_mod = glmnet(X, y, alpha = 1, lambda = 0.001)

coef(lasso_mod)
plot(lasso_mod)
legend("bottomright", lwd = 1, col = 1:11, legend = colnames(X), cex = .7)
bestlam <- lasso_mod$lambda.min
lasso.pred <- predict(lasso_mod, s = bestlam, newx = X[,])
lasso.coef  <- predict(lasso_mod, type = 'coefficients', s = bestlam)
lasso.coef
```
Lasso fixed normality but not hetero
```{r}
test_model <- lm(y ~ x2+x3+x5+x10, data = winex)
shapiro.test(test_model$coefficients)
fligner.test(test_model$residuals, wine$Group)
```

TRYING POLYNOMIAL ON FB Selection 
```{r}
FB.model.BIC$coefficients
with_int <- lm(y ~ x2 + x5+x7+x9+x10+x11+x9*x11, data = winex)
shapiro.test(with_int$residuals)
fligner.test(with_int$residuals,wine$Group)
test$coefficients
plot(winex$x11,winex$y)
plot(winex$x10,winex$y)
plot(winex$x9,winex$y)
plot(winex$x7,winex$y)
plot(winex$x5,winex$y)
plot(winex$x2,winex$y)
corrplot(datamatrix,method = "number") #potential cor with 9 and 11
shapiro.test(FB.model.BIC$residuals)
fligner.test(FB.model.BIC$residuals, wine$Group)
plot(FB.model.BIC$fitted.values, FB.model.BIC$residuals)
```

```{r}
columns <- c(2,5,7,9,10,11,12)
centered <- winex[,columns]
for (x in 1:6){
  centered[,x] <- centered[,x] - mean(centered[,x])
}
no_poly <- lm(y~., data = centered)

#x11 poly
p1 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x11^2), data = centered)
p2 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x11^2)+I(x11^3), data = centered)
anova(p1,p2) #so since both anovas significant, test assumptions again with p2
anova(no_poly,p2) 
shapiro.test(p2$residuals) #no improvement
fligner.test(p2$residuals, wine$Group) #improved fk a lot

#x9 poly - pretty much same as x11 poly
c1 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x9^2), data = centered)
c2 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x9^2)+I(x9^3), data = centered)
anova(c1,c2) #so since both anovas significant, test assumptions again with p2
anova(no_poly,c2) 
shapiro.test(c2$residuals) #no improvement
fligner.test(c2$residuals, wine$Group) #improved fk a lot

#so far this on performed best
b1 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x11^2) + I(x9^2), data = centered)
b2 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x11^2)+I(x11^3) + I(x9^3) + I(x9), data = centered)
anova(b1,b2) #so since both anovas significant, test assumptions again with p2
anova(no_poly,b2) 
shapiro.test(b2$residuals) #no improvement
fligner.test(b2$residuals, wine$Group) #improved fk a lot


```

Testing lasso coef with poly
```{r}
test_model <- lm(y ~ x2+x3+x5+x10, data = winex)
input <- c(2,3,5,10)
Lcentered <- winex[,input]
for (x in 1:4){
  Lcentered[,x] <- Lcentered[,x] - mean(Lcentered[,x])
}

noL_poly <- lm(y~., data = Lcentered)
shapiro.test(noL_poly$residuals)
fligner.test(noL_poly$residuals,wine$Group)

n1 <- lm(y~x2+x3+x5+x10+I(x10^2),data = Lcentered)
n2 <- lm(y~x2+x3+x5+x10+I(x10^2)+I(x10^3),data = Lcentered)
anova(n1,n2)
shapiro.test(n2$residuals) 
fligner.test(n2$residuals, wine$Group)

```


```{r}

```

```{r}
BC.xdata <- BC.data
BC.xdata <- BC.xdata[,-13]
colnames(BC.xdata) <- c("y","x1","x2","x3","x4","x5","x6","x7","x8","x9","x10","x11")

#FB bic with BC - not more effective than jsut bc
empty_model2 <- lm(y ~ 1, data = BC.xdata)
full_model2 <- lm(y ~ ., data = BC.xdata)
FBBC.BIC = stepAIC(empty_model2,  scope = list(lower = empty_model2, upper= full_model2), k = log(nrow(winex)),trace=FALSE,direction = "both")
shapiro.test(FBBC.BIC$residuals)
fligner.test(FBBC.BIC$residuals, BC.data$Group)

#lasso variables with BC
BCcenter <- BC.xdata
for (x in 2:11){
  BCcenter[,x] <- BCcenter[,x] - mean(BCcenter[,x])
}
LBC <- lm(y ~ x2+x7+x5+x9+x11+x10+I(x2^2)+I(x2^3), data = BCcenter)
shapiro.test(LBC$residuals)
fligner.test(LBC$residuals, BC.data$Group)
```

log transform
```{r}
winexlog <- winex
winexlog$y <- (winexlog$y)^(1/3)

empty_model3 <- lm(y ~ 1, data = winexlog)
full_model3 <- lm(y ~ ., data = winexlog)
logm = stepAIC(empty_model3,  scope = list(lower = empty_model3, upper= full_model3), k = log(nrow(winex)),trace=FALSE,direction = "both")

Group = rep("Lower",nrow(wine)) #Creates a vector that repeats "Lower" n times
Group[winexlog$y > median(winexlog$y)] = "Upper" #Changing the appropriate values to "Upper"
Group = as.factor(Group) #Changes it to a factor, which R recognizes as a grouping variable.
winexlog$Group = Group

shapiro.test(logm$residuals)
fligner.test(logm$residuals, winexlog$Group)

lm(y ~ x2+x3+x5+x10, data = winex)
#now with poly
cube1 <- lm(y ~ x2+x3+x5+x10, data = winexlog)
shapiro.test(cube1$residuals)
fligner.test(cube1$residuals,winexlog$Group)
```

Reworking leverage
```{r}
#leverage point plus outliers
wine[outliers,]
wine[lev.hat,]
OL <- c(lev.hat,outliers)
wine_NOL <- wine[-OL,]

Group = rep("Lower",nrow(wine_NOL)) #Creates a vector that repeats "Lower" n times
Group[wine_NOL$quality > median(wine_NOL$quality)] = "Upper" #Changing the appropriate values to "Upper"
Group = as.factor(Group) #Changes it to a factor, which R recognizes as a grouping variable.
wine_NOL$Group = Group

wine_NOL_ng <- wine_NOL[,-13]
colnames(wine_NOL_ng) <- c("x1","x2","x3","x4","x5","x6","x7","x8","x9","x10","x11","y")
empty_model4 <- lm(y ~ 1, data = wine_NOL_ng)
full_model4 <- lm(y ~ ., data = wine_NOL_ng)

FBNOL = stepAIC(empty_model4,  scope = list(lower = empty_model4, upper= full_model4), k = log(nrow(wine_NOL)),trace=FALSE,direction = "both")

shapiro.test(FBNOL$residuals)
fligner.test(FBNOL$residuals,wine_NOL$Group)
FBNOL$coefficients

#now with polyw


please <- lm(y~x2+x3+x7+x9+x10+x11+x11*x10, data = wine_NOL_ng)
shapiro.test(please$residuals)
fligner.test(please$residuals,wine_NOL$Group)


nol_center <- wine_NOL_ng
for (x in 1:11){
  nol_center[,x] <- nol_center[,x] - mean(nol_center[,x])
}

hm <- lm(y~x2+x7+x10+I(x10^2)+I(x10^3), data = nol_center)
shapiro.test(hm$residuals)
fligner.test(hm$residuals,wine_NOL$Group)
```

ROUND UP OR DOWN AND THEN TEST ASSUMPTIONS

SO FAR HERE ARE THE BEST MODELS
```{r}
#FB selection coef with x11 poly - better FK
p2 <- lm(y ~ x2+x5+x7+x9+x10+x11+I(x11^2)+I(x11^3), data = centered)
shapiro.test(p2$residuals)$p 
fligner.test(p2$residuals, wine$Group)$p.value

#lasso variables - better normality
test_model <- lm(y ~ x2+x3+x5+x10, data = winex)
shapiro.test(test_model$residuals)
fligner.test(test_model$residuals, wine$Group)

#lasso variables with BC
LBC <- lm(y ~ x2+x7+x5+x9+x11+x10+I(x2^2)+I(x2^3), data = BCcenter)
shapiro.test(LBC$residuals)
fligner.test(LBC$residuals, BC.data$Group)

#outlier and leverage removed
please <- lm(y~x2+x3+x7+x9+x10+x11+x11*x10, data = wine_NOL_ng)
shapiro.test(please$residuals)
fligner.test(please$residuals,wine_NOL$Group)

results <- data.frame("Model" = c("FB Poly",
                                  "Lasso",
                                  "Lasso + BC",
                                  "Lasoo+NoL"),
                      "Shapiro" = c(shapiro.test(p2$residuals)$p,
                                    shapiro.test(test_model$residuals)$p,
                                    shapiro.test(LBC$residuals)$p,
                                    shapiro.test(please$residuals)$p),
                      "FK" = c(fligner.test(p2$residuals, wine$Group)$p.value,
                               fligner.test(test_model$residuals, wine$Group)$p.value,
                               fligner.test(LBC$residuals, BC.data$Group)$p.value,
                               fligner.test(please$residuals,wine_NOL$Group)$p.value)
                      )
results
```

trying to round 
```{r}
p2 #FB poly
test_model #lasso
LBC #lasso on BC transform
please #outlier/leverage removed, lasso plus interaction


aa <- p2_vec >= 3 & p2_vec < 3.5
bb <- p2_vec >= 3.5 & p2_vec < 4
cc <- p2_vec >= 4 & p2_vec < 4.5
dd <- p2_vec >= 4.5 & p2_vec < 5
ee <- p2_vec >= 5 & p2_vec < 5.5
ff <- p2_vec >= 5.5 & p2_vec < 6
gg <- p2_vec >= 6 & p2_vec < 6.5
hh <- p2_vec >= 6.5 & p2_vec < 7
ii <- p2_vec >= 7 & p2_vec < 7.5
jj <- p2_vec >= 7.5 & p2_vec <= 8

p2_vec <- as.double(p2[[5]])

# Apply ceiling to elements that meet the condition
p2_vec[aa] <- floor(p2_vec[aa])
p2_vec[bb] <- ceiling(p2_vec[bb])
p2_vec[cc] <- floor(p2_vec[cc])
p2_vec[dd] <- ceiling(p2_vec[dd])
p2_vec[ee] <- floor(p2_vec[ee])
p2_vec[ff] <- ceiling(p2_vec[ff])
p2_vec[gg] <- floor(p2_vec[gg])
p2_vec[hh] <- ceiling(p2_vec[hh])
p2_vec[ii] <- floor(p2_vec[ii])
p2_vec[jj] <- ceiling(p2_vec[jj])

p2_vec_residuals <- wine$quality - p2_vec
shapiro.test(p2_vec_residuals)
fligner.test(p2_vec_residuals, wine$Group)


test_model_vec <- test_model$fitted.values
test_model_vec[aa] <- floor(test_model_vec[aa])
test_model_vec[bb] <- ceiling(test_model_vec[bb])
test_model_vec[cc] <- floor(test_model_vec[cc])
test_model_vec[dd] <- ceiling(test_model_vec[dd])
test_model_vec[ee] <- floor(test_model_vec[ee])
test_model_vec[ff] <- ceiling(test_model_vec[ff])
test_model_vec[gg] <- floor(test_model_vec[gg])
test_model_vec[hh] <- ceiling(test_model_vec[hh])
test_model_vec[ii] <- floor(test_model_vec[ii])
test_model_vec[jj] <- ceiling(test_model_vec[jj])
test_model_vec_residuals <- wine$quality - test_model_vec

shapiro.test(test_model_vec_residuals)
fligner.test(test_model_vec_residuals, wine$Group) #ACTUAL CONSTANTCY


LBC_vec <- LBC$fitted.values
LBC_vec[aa] <- floor(LBC_vec[aa])
LBC_vec[bb] <- ceiling(LBC_vec[bb])
LBC_vec[cc] <- floor(LBC_vec[cc])
LBC_vec[dd] <- ceiling(LBC_vec[dd])
LBC_vec[ee] <- floor(LBC_vec[ee])
LBC_vec[ff] <- ceiling(LBC_vec[ff])
LBC_vec[gg] <- floor(LBC_vec[gg])
LBC_vec[hh] <- ceiling(LBC_vec[hh])
LBC_vec[ii] <- floor(LBC_vec[ii])
LBC_vec[jj] <- ceiling(LBC_vec[jj])
LBC_vec_residuals <- wine$quality - LBC_vec
shapiro.test(LBC_vec_residuals)
fligner.test(LBC_vec_residuals, BC.data$Group)

please_vec <- please$fitted.values
please_vec[aa] <- floor(please_vec[aa])
please_vec[bb] <- ceiling(please_vec[bb])
please_vec[cc] <- floor(please_vec[cc])
please_vec[dd] <- ceiling(please_vec[dd])
please_vec[ee] <- floor(please_vec[ee])
please_vec[ff] <- ceiling(please_vec[ff])
please_vec[gg] <- floor(please_vec[gg])
please_vec[hh] <- ceiling(please_vec[hh])
please_vec[ii] <- floor(please_vec[ii])
please_vec[jj] <- ceiling(please_vec[jj])
please_vec_residuals <- wine_NOL$quality - please_vec

shapiro.test(please_vec_residuals)
fligner.test(please_vec_residuals, wine_NOL$Group)
```

BEST MODEL THUS FAR
```{r}
test_model_vec <- test_model$fitted.values
test_model_vec[aa] <- floor(test_model_vec[aa])
test_model_vec[bb] <- ceiling(test_model_vec[bb])
test_model_vec[cc] <- floor(test_model_vec[cc])
test_model_vec[dd] <- ceiling(test_model_vec[dd])
test_model_vec[ee] <- floor(test_model_vec[ee])
test_model_vec[ff] <- ceiling(test_model_vec[ff])
test_model_vec[gg] <- floor(test_model_vec[gg])
test_model_vec[hh] <- ceiling(test_model_vec[hh])
test_model_vec[ii] <- floor(test_model_vec[ii])
test_model_vec[jj] <- ceiling(test_model_vec[jj])
test_model_vec_residuals <- wine$quality - test_model_vec

shapiro.test(test_model_vec_residuals)
fligner.test(test_model_vec_residuals, wine$Group) 
plot(test_model_vec_residuals, wine$quality)
test_model$coefficients
qqnorm(test_model_vec_residuals)
qqline(test_model_vec_residuals)
```

ACTUAL BEST MODELS
```{r}
#removing vif variables then model selection and rounding
before$coefficients
shapiro.test(before_vec_residuals)
fligner.test(before_vec_residuals, wine$Group)

#lasso variables and rounding
test_model$coefficients
shapiro.test(test_model_vec_residuals)
fligner.test(test_model_vec_residuals, wine$Group)

#log transform on x's plus fb selection
logfb$coefficients
shapiro.test(logfb$residuals)
fligner.test(logfb$residuals, wine$Group)

#above with rounding
shapiro.test(logfb_vec_residuals)
fligner.test(logfb_vec_residuals, wine$Group)

#same as above but with rounding and removing VIF>2.5
logfbrem$coefficients
shapiro.test(logfbrem_vec_residuals)
fligner.test(logfbrem_vec_residuals, wine$Group)
```

TUKEY on x's
```{r}
tukeyx1 <- transformTukey(winex$x1, plotit = F)
tukeyx2 <- transformTukey(winex$x2, plotit = F)
tukeyx3 <- transformTukey(winex$x3, plotit = F)
tukeyx4 <- transformTukey(winex$x4, plotit = F)
tukeyx5 <- transformTukey(winex$x5, plotit = F)
tukeyx6 <- transformTukey(winex$x6, plotit = F)
tukeyx7 <- transformTukey(winex$x7, plotit = F)
tukeyx8 <- transformTukey(winex$x8, plotit = F)
tukeyx9 <- transformTukey(winex$x9, plotit = F)
tukeyx10 <- transformTukey(winex$x10, plotit = F)
tukeyx11 <- transformTukey(winex$x11, plotit = F)
tukeyy <- transformTukey(winex$y, plotit = F)
T.Data = data.frame(y = tukeyy,
                    x1 = tukeyx1,
                    x2 = tukeyx2,
                    x3 = tukeyx3,
                    x4 = tukeyx4,
                    x5 = tukeyx5,
                    x6 = tukeyx6,
                    x7 = tukeyx7,
                    x8 = tukeyx8,
                    x9 = tukeyx9,
                    x10 = tukeyx10,
                    x11 = tukeyx11)

eeeme <- lm(y~1, data = T.Data)
ffffmf <- lm(y~., data = T.Data)
tuke = stepAIC(eeeme,  scope = list(lower = eeeme, upper= ffffmf), k = log(nrow(winex)),trace=FALSE,direction = "both")
Group = rep("Lower",nrow(wine)) #Creates a vector that repeats "Lower" n times
Group[T.Data$y > median(T.Data$y)] = "Upper" #Changing the appropriate values to "Upper"
Group = as.factor(Group) #Changes it to a factor, which R recognizes as a grouping variable.
T.Data$Group = Group
shapiro.test(tuke$residuals)
fligner.test(tuke$residuals,T.Data$Group)
```

Try some basic transformations on the x variables
```{r}
hist(wine$volatile.acidity)
hist(winex$x3)
hist(winex$x7)
hist(winex$x5)
hist(winex$x10)
logwinex <- winex
logwinex$x1 <- log(winex$x1)
logwinex$x2 <- log(winex$x2)
logwinex$x3 <- (winex$x3)^1/2
logwinex$x7 <- log(winex$x7)
logwinex$x5 <- log(winex$x5)
logwinex$x6 <- log(winex$x6)
logwinex$x10 <- log(winex$x10)
logwinex$x11 <- log(winex$x11)
best2 <- lm(y~x2+x7+x5+x10, data = logwinex)
best1 <- lm(y~x2+x3+x5+x10, data = logwinex)
shapiro.test(best2$residuals)
fligner.test(best2$residuals, wine$Group)
shapiro.test(best1$residuals)
fligner.test(best1$residuals, wine$Group)

```

```{r}
#no need for 8,9,4, log with fb selection
eeeem <- lm(y~1, data = logwinex)
fffffm <- lm(y~., data = logwinex)
logfb = stepAIC(eeeem,  scope = list(lower = eeeem, upper= fffffm), k = log(nrow(winex)),trace=FALSE,direction = "both")
shapiro.test(logfb$residuals)
fligner.test(logfb$residuals, wine$Group)
logfb$coefficients #remove x11,x9 for vif - NOPE
logfbrem <- lm(y~x2+x10+x5+x9+x6+x7, data = logwinex)
shapiro.test(logfbrem$residuals)
fligner.test(logfbrem$residuals, wine$Group)



#rounding
logfb_vec <- as.double(logfb[[5]])

# Apply ceiling to elements that meet the condition
logfb_vec[aa] <- floor(logfb_vec[aa])
logfb_vec[bb] <- ceiling(logfb_vec[bb])
logfb_vec[cc] <- floor(logfb_vec[cc])
logfb_vec[dd] <- ceiling(logfb_vec[dd])
logfb_vec[ee] <- floor(logfb_vec[ee])
logfb_vec[ff] <- ceiling(logfb_vec[ff])
logfb_vec[gg] <- floor(logfb_vec[gg])
logfb_vec[hh] <- ceiling(logfb_vec[hh])
logfb_vec[ii] <- floor(logfb_vec[ii])
logfb_vec[jj] <- ceiling(logfb_vec[jj])

logfb_vec_residuals <- wine$quality - logfb_vec
shapiro.test(logfb_vec_residuals)
fligner.test(logfb_vec_residuals, wine$Group)



logfbrem_vec <- as.double(logfbrem[[5]])

# Apply ceiling to elements that meet the condition
logfbrem_vec[aa] <- floor(logfbrem_vec[aa])
logfbrem_vec[bb] <- ceiling(logfbrem_vec[bb])
logfbrem_vec[cc] <- floor(logfbrem_vec[cc])
logfbrem_vec[dd] <- ceiling(logfbrem_vec[dd])
logfbrem_vec[ee] <- floor(logfbrem_vec[ee])
logfbrem_vec[ff] <- ceiling(logfbrem_vec[ff])
logfbrem_vec[gg] <- floor(logfbrem_vec[gg])
logfbrem_vec[hh] <- ceiling(logfbrem_vec[hh])
logfbrem_vec[ii] <- floor(logfbrem_vec[ii])
logfbrem_vec[jj] <- ceiling(logfbrem_vec[jj])

logfbrem_vec_residuals <- wine$quality - logfbrem_vec
shapiro.test(logfbrem_vec_residuals)
fligner.test(logfbrem_vec_residuals, wine$Group)
```

Final Model
```{r}
logfbrem$coefficients
shapiro.test(logfbrem_vec_residuals)
fligner.test(logfbrem_vec_residuals, wine$Group)
qqnorm(logfb_vec_residuals)
qqline(logfb_vec_residuals)
plot(x = wine$quality, y = logfb_vec_residuals, main = "Residual Plot", xlab = "Quality", ylab = "Residuals")
abline(h = 0, col = "red", lwd = 2)
```
